---
title: "README"
output:
  rmarkdown::github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/README-",
  message = FALSE, warning = FALSE
)
```

# CGDRO

CGDRO is an R package providing conprehensive multi-source prediction and model statistical inference without knowing target labels, offering multi-source solutions to low-dimensional and high-dimensional, linear and complex data, regression and classification problems. 

# Installation

The development version from [GitHub](https://github.com) with:
```{r}
# install.packages("devtools")
devtools::install_github("jaon11/CGDRO")
```

# Example
This is a basic example which shows you how to solve a common problem:

```{r}
library(CGDRO)
```

The data is heterogeneous and covariates shift between source and target data
```{r}
# number of source groups = 3, with 1000 samples each
  # sigma: source group 1,3: 0.5; source group 2: 2
  # target sample size = 10000
  # dimension p = 5
  data <- simu_linear_reg_lowd(n_list = list(1000,1000,1000), N=10000, p = 5, seed = 123)
  Xlist = data$X_list
  Ylist = data$Y_list
  X0 = data$X0
```

Fitting CGDRO model for low-dimensional linear regression with reward loss and summarize results
```{r}
  ## fit cgdro
  ## Note: only when loss_type='reward', infer() can be called to get confidence intervals
  ## For other loss_type, only point estimation and prediction can be done
  fit <- cgdro_(Xlist, Ylist, X0, loss_type = "reward",
               family = "reg_ld",  intercept = TRUE,
               delta = 0,  verbose = FALSE)
  inf <- infer_cgdro_(fit, M = 200, alpha = 0.05)
  ## summary
  summary_cgdro_(fit, infer=inf)
```

Make prediction on target data
```{r}
  ## predict
  pred <- predict_cgdro_(fit)  # N x 1 vector of predicted values
  head(pred)
```


